Concurrent Hash Tables in Java

### 2022-03-25 paper.tex
Ignore .toc
Basic sections

\begin{document}
\author{Dalton Kajander, Shawn Guydeene, Blake Lastname}
\title{Concurrent Hash Tables in Java}
\date{\today{}}

\maketitle

\begin{lstlisting}[language={Java},caption=Testing surce code in \LaTeX{}.,breaklines=true,frame=single]
class HashTableCon {
    public static void main(String[] args) {
        bool isConcurrent = true;
    }
}
\end{lstlisting}

>>>>

\begin{document}
\author{Dalton Kajander, Shawn Guydeene, Blake Lastname}
\title{Concurrent Hash Tables in Java}
\date{\today{}}
\maketitle

\newpage
\tableofcontents
\newpage

\section{The Problem}
What problem?

\section{Research}
Oh, that problem.

\section{Related work}
I've seen a similar problem before

\section{Contributions}
I've fixed this problem once

\section{Algorithms}
And this is how I did it!
\begin{lstlisting}[language={Java},caption=Testing surce code in \LaTeX{}.,breaklines=true,frame=single]
class HashTable<T> {
    bool isConcurrent;
    public static void main(String[] args) {
        isConcurrent = true;
    }

    public HashTable<T>(bool isConcurrent) {
        this.isConcurrent = isConcurrent;
    }
}
\end{lstlisting}

\section{Experimental Results}
Well, it worked on my machine.
